Follow-up Samples

### 2017-01-03 submission/supplemental_outline_20161024.Rmd
update supplemental figures to include paired wilcoxson

@@

ggsave(file = "../results/figures/FigureS1.pdf", time_graph, 
       width=6, height = 8, dpi = 300)
```

>>>>

paired_table <- read.csv("../results/tables/OTU_paired_wilcoxson_test.csv", header = T, stringsAsFactors = F)

label_names <- c("Full Data Set", "Adenoma Only", "CRC Only")
names(label_names) <- c("ALL", "adn", "crc")

pvalue_distribution_paired <- ggplot(paired_table, aes(x=BH_corrected)) + geom_histogram() + 
  geom_vline(aes(xintercept = 0.05, color = "red"), linetype = 2, size = 1) + 
  facet_wrap(~factor(analysis, levels = c("ALL", "adn", "crc")), 
             labeller = as_labeller(label_names)) + theme_bw() + 
  xlab("Benjamini-Hochberg Corrected P-values") + ylab("Counts") + 
  theme(legend.position = "none")

ggsave(file = "../results/figures/FigureS1.pdf", pvalue_distribution_paired, 
       width=12, height = 6, dpi = 300)

```{r supplemental_figure2, echo=FALSE, message=FALSE, warning=FALSE}

@@

ggsave(file = "../results/figures/FigureS2.pdf", time_graph, 
       width=6, height = 8, dpi = 300)
```
